Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-10-05 ms.tex

\begin{figure}[ht!]
\epsscale{0.7}
%\plotone{plots/slv1coadd.pdf}
%\plotone{plots/slv2coadd.pdf}
%\plotone{plots/onewcoadd.pdf}\\
\plotone{plots/streak_length_v_deltam.pdf}
\epsscale{1}
\caption{The trade off between pixels lost to streaks and final median coadded depth of the survey. Points to the right of the dashed line show improvement while those to the left signify the regained pixels do not adequatly compensate for the lost depth. In no situation are we able to prevent depth loss in at least some filters. \label{fig-trade-off}
XXX--the top panels have more info, but I kinda like the lower for the simplicity. Maybe just the lower and say all the filters follow a similar trend? Or a plot for g and a plot for i?
xxx--MR deleted the top panels, and thinks we should avoid discussing filters/bands too much because people will ask whether we are simulating sat brightness as a function of wavelength... which we definitely aren't}
\end{figure}

>>>>

\begin{figure}[ht!]
\epsscale{0.7}
\plotone{plots/streak_length_v_deltam.pdf}
\epsscale{1}
\caption{The trade off between pixels lost to streaks and final median coadded depth of the survey. XXX--change y-axis to fraction of pixels. \label{fig-trade-off}}
\end{figure}
